The problem and promise of scale in multilayer networks

### 2020-01-28 paper/manuscript.Rmd
metric section

For each multilayer network, we calculated XXX metrics.These included four neighborhood-based metrics: degree centrality, multidegree, degree deviation, and neighbours as well as two multilayer [need better term here?] metrics: connective redundancy and relevance (see Glossary for definitions). GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON EXPLAINING THESE).

We generated all networks 
Right now, we calculate mostly degree/neighborhood based metrics.

Reference for extending degree centrality to multilayer, neighbors, connective redundancy and relevance: Berlingerio 2011 "Foundations of multidimensional..."

@@

* Neighbors/neighborhood (number of unique actors directly connected to each focal)

Neighbors = degree within a network layer
But across a multilayer network with multiple layers, some neighbors are repeated.

So the difference between neighbors and degree is the basis for

@@

>>>>

#### Network metrics

For each multilayer network, we calculated four metrics.These included: multidegree, graph strength, redundancy/relevance, and  layer similarity.  GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON EXPLAINING THESE).

ALR: Reference for extending degree centrality to multilayer, neighbors, connective redundancy and relevance: Berlingerio 2011 "Foundations of multidimensional..."

##### Multidegree

@@

* Neighbors/neighborhood (number of unique actors directly connected to each focal)
Neighbors = degree within a network layer
But across a multilayer network with multiple layers, some neighbors are repeated.

##### Graph strength

##### Redundancy/relevance

@@

##### Layer similarity
